---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# defogger <a href="https://andrewallenbruce.github.io/defogger/"><img src="man/figures/logo.svg" align="right" height="139" /></a>

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/defogger/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/defogger/actions/workflows/R-CMD-check.yaml)
[![repo status:
WIP](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

The goal of defogger is to provide a collection of reliable open-source tools to work with Transparency in Coverage (TiC) files.

## Installation

You can install the development version of defogger from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/defogger")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(defogger)
## basic example code
```



## Code of Conduct

Please note that the defogger project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/defogger/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
