---
title: "defogger"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{defogger}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  tidy = "styler",
  comment = "#>",
  dpi = 72, 
  out.width = "100%",
  dev = "png",
  dev.args = list(png = list(type = "cairo-png")),
  optipng = "-o1 -quiet",
  error = TRUE
)

library(defogger)
```

This vignette provides an introduction to the basic functionality included in the package.

<br><br>

# Problem Statement

The Transparency in Coverage files only include the NPI of the provider.

## Using the `defog_toc()` Function

```{r}
# Load package
library(defogger)

# Assign TiC file link to object
centene_url <- "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-06-29_ambetter_index.json"

# Retrieve file with defog_get() function
centene_results <- defog_toc(centene_url) |> 
  dplyr::slice_head(n = 10)

#----This returns a tibble of 2,598 rows so, 
#----in the interest of space, we'll look at the first 10

# View first 10 rows of result
centene_results
```

<br>

`defog_toc_centene()` is the first of many helper functions, included here to differentiate between Centene as the reporting entity (third party administrator) and it's two sub-entities, Ambetter and Magellan:

<br>

```{r}
# Add reporting entity and sub-entity
centene_results <- defog_toc_centene(centene_results)

# View results
centene_results
```

<br>

Next, we need to download the Out-of-Network (OON) and In-Network (INN) files.

## Using the `defog_oon()` Function

From the results above, we can filter to the `out_of_network` files and choose a state. California's the only state in the first 10 rows so we'll go with CA:

<br>

```{r}
# Filter to OON California URL
centene_oon_CA_url <- centene_results |> 
  dplyr::filter(rate_type == "out_of_network") |> 
  dplyr::filter(state == "CA") |> 
  dplyr::select(location) |> 
  dplyr::distinct() |> 
  tibble::deframe()

# View URL
centene_oon_CA_url
```

<br>

Next, plug the URL object into the `defog_oon()` function and retrieve the file:

```{r}
# Retrieve the file
centene_oon_CA_results <- defog_oon(centene_oon_CA_url) |> dplyr::slice_head(n = 10)

# View results
centene_oon_CA_results
```

<br>

This returns all of the information required by the Transparency in Coverage rule. However, simply having a provider's NPI isn't very helpful for analysis. Where do they practice? What specialty are they? Are they part of an organization or just an individual? This is where the NPPES NPI Registry Search comes in.

<br>

## Using the `defog_npi()` Function

First, we need to isolate the distinct NPIs from the `out_of_network` results above and unlist them. There are 247 so we'll take the first 10 to keep this example as lightweight as we can:

<br>

```{r}
# Filter to distinct NPIs and unlist
centene_oon_CA_npi <- centene_oon_CA_results |> 
  dplyr::distinct(npi) |> 
  dplyr::slice_head(n = 10) |> 
  unlist(use.names = FALSE)

# View results
centene_oon_CA_npi
```

<br>

Then pipe them into the NPPES search function, `defog_npi()`:

```{r}
centene_oon_CA_npi2 <- centene_oon_CA_npi |> 
  purrr::map_dfr(defog_npi)

# View results
centene_oon_CA_npi2
```


```{r}
# Start with base df and unnest first level
start <- centene_oon_CA_npi2 |>
  dplyr::filter(outcome == "results") |>
  tidyr::unnest(data_lists)

# Isolate the NPI and datetime
search <- start |>
  dplyr::select(search:datetime) |>
  dplyr::mutate(id = search) |>
  dplyr::select(id, datetime)

## || CREATE ID KEY
key <- search |>
  dplyr::select(id) |>
  unlist(use.names = FALSE)

# Rename number & enumeration type
basic_1 <- start |>
  dplyr::select(
    prov_type = enumeration_type,
    npi = number) |>
  dplyr::mutate(
    npi = as.character(npi),
    id = key) |>
  dplyr::relocate(id)

# Basic section
basic_2 <- start |>
  dplyr::select(basic) |>
  tidyr::unnest(basic) |>
  dplyr::mutate(id = key) |>
  dplyr::relocate(id)

# Join Columns
basic <- dplyr::full_join(basic_1, basic_2, by = "id")

# Isolate lists
lists <- start |>
  dplyr::select(!(basic)) |>
  dplyr::select(where(~ is.list(.x) && 
  (insight::is_empty_object(.x) == FALSE))) |> 
  dplyr::mutate(id = key)

# Replace Empty Lists with NA
lists[apply(lists, 2, function(x) lapply(x, length) == 0)] <- NA

# List names for identification
ls_names <- tibble::enframe(names(lists))

#--------------- BEGIN LISTS

# Addresses section
addresses <- lists |>
  dplyr::select(id, addresses) |>
  tidyr::unnest(cols = c(addresses))

# Join Columns
#basic_add <- dplyr::full_join(basic, addresses, by = "id")

# Taxonomies
taxonomies <- lists |>
  dplyr::select(id, taxonomies) |>
  tidyr::unnest(cols = c(taxonomies)) |> 
  datawizard::data_addprefix("tax_", exclude = "id")

# Join Columns
#basic_add_tax <- dplyr::full_join(basic_add, taxonomies, by = "id")

# Identifiers
identifiers <- lists |>
  dplyr::select(id, identifiers) |> 
  tidyr::unnest(cols = c(identifiers)) |> 
  datawizard::data_addprefix("id_", exclude = "id")

# Join Columns
#basic_add_tax_id <- dplyr::full_join(basic_add_tax, identifiers, by = "id")

# Practice Locations
practiceLocations <- lists |>
  dplyr::select(id, practiceLocations) |> 
  tidyr::unnest(cols = c(practiceLocations)) |> 
  datawizard::data_addprefix("pracloc_", exclude = "id")

# Other Names
other_names <- lists |>
  dplyr::select(id, other_names) |> 
  tidyr::unnest(cols = c(other_names)) |> 
  datawizard::data_addprefix("other_", exclude = "id")

```

<br>

Next, we can clean up the results with the `prov_nppes_npi_clean()` function:

<br>

```{r}
centene_oon_CA_npi3 <- centene_oon_CA_npi2 |> 
  dplyr::group_split(search) |> 
  purrr::map_dfr(prov_nppes_npi_clean)

centene_oon_CA_npi3
```


```{r}
# View results
# centene_oon_CA_npi3
```


## Pivot Columns Wide with `prov_nppes_npi_clean2()`

```{r}
# centene_oon_CA_npi_wide <- prov_nppes_npi_clean2(centene_oon_CA_npi3)
# 
# centene_oon_CA_npi_wide
```

Then join the two frames for the final output:

```{r}
# centene_oon_CA_join <- dplyr::full_join(
#   centene_oon_CA_results, 
#   centene_oon_CA_npi_wide)
# 
# centene_oon_CA_join
```




<br><br>
