---
title: "Working with Large Data"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  comment = "#>",
  dpi = 72, 
  out.width = "100%",
  dev = "png",
  dev.args = list(png = list(type = "cairo-png")),
  optipng = "-o1 -quiet",
  error = TRUE
)
```

<br>

These files come from [Centene Corporation](https://www.centene.com/price-transparency-files.html)'s Transparency in Coverage site.

<br>

```{r}
library(dplyr)
library(purrr)
library(dm)
library(defogger)
```

<br>

# Build the Centene TOC Table

<br>

```{r}
centene_toc_urls <- data.frame(
  entity = c("Centene"),
  sub_entity = c("Ambetter", 
                "Fidelis", 
                "QualChoice", 
                "HealthNet", 
                "MHN", 
                "WellCare_NC"),
  type = c("toc"),
  origin = c("https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_ambetter_index.json", 
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_fidelis_index.json",
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_qualchoice_index.json",
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_healthnet_index.json",
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_mhn_index.json",
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_wellcarenc_index.json"))
```

```{r echo=FALSE}
centene_toc_urls
```
<br><br>

## QualChoice TOC Sub-indices

```{r}
centene_toc_qualchoice_subs <- data.frame(
  entity = c("Centene"),
  sub_entity = c("QualChoice"),
  sub_index = c("Alf",
                "Arnold_Bevins",
                "Hot_Springs",
                "Dillards",
                "JV_Manufacturing",
                "Royal_Financial"),
  type = c("toc"),
  origin =   c("https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_qualchoice_alf_index.json",
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_qualchoice_arnold_and_blevins_index.json",
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_qualchoice_city_of_hot_springs_index.json",
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_qualchoice_dillards_index.json",
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_qualchoice_jv_manufacturing_index.json",
               "https://www.centene.com/content/dam/centene/Centene%20Corporate/json/DOCUMENT/2022-08-30_qualchoice_royal_financial_index.json"))
```

```{r echo=FALSE}
centene_toc_qualchoice_subs
```

<br><br>

## Final TOC Table

```{r}
toc_url_centene <- dplyr::full_join(centene_toc_urls, 
                                    centene_toc_qualchoice_subs, 
                                    by = c("entity", 
                                           "sub_entity", 
                                           "type", 
                                           "origin"), copy = TRUE) |> 
                   dplyr::relocate(sub_index, .after = "sub_entity")
```


```{r echo=FALSE}
toc_url_centene
```
# Build the Centene RESP Table

```{r}
toc_resp_centene <- toc_url_centene |> 
                    dplyr::select(origin) |>
                    dplyr::distinct() |> 
                    tibble::deframe() |> 
                    purrr::map_dfr(defog_toc)

toc_resp_centene <- toc_resp_centene |> 
                    dplyr::rename(type = rate_type) |> 
                    dplyr::mutate(entity = dplyr::case_when(
                    entity == "Centene Management Company LLC" ~ "Centene", 
                    TRUE ~ entity))
```

```{r echo=FALSE}
toc_resp_centene
```

<br><br>

# Creating a Relational Database with `dm`

You can build a relational database in R with the {dm} package, using only data frames in your R environment. Once your data model is complete, you can deploy it to a range of database management systems (DBMS). First, we need to create a dm object:

```{r}
dm_centene_no_keys <- dm::dm(toc_url_centene, toc_resp_centene)
```

```{r echo=FALSE}
dm_centene_no_keys
```

<br><br>

Next, we need to define the primary keys:

```{r}
dm::dm_enum_pk_candidates(dm = dm_centene_no_keys, table = toc_url_centene)
```

```{r}
dm_centene_only_pks <- dm_centene_no_keys |> dm::dm_add_pk(table = toc_url_centene, columns = origin)
```


```{r echo=FALSE}
dm_centene_only_pks
```
<br><br>

Now, we need to link the two tables by a foreign key:

```{r}
dm::dm_enum_fk_candidates(dm = dm_centene_only_pks, table = toc_resp_centene, ref_table = toc_url_centene)
```

```{r}
dm_centene_all_keys <- dm_centene_only_pks |> dm::dm_add_fk(table = toc_resp_centene, columns = origin, ref_table = toc_url_centene)
```


```{r echo=FALSE}
dm_centene_all_keys
```
<br><br>

## Visualizing the Data Model

```{r}
dm_centene_no_keys |> dm::dm_draw(rankdir = "TB", view_type = "all")
```

```{r}
dm_centene_only_pks |> dm::dm_draw(rankdir = "TB", view_type = "all")
```

```{r}
dm_centene_all_keys |> dm::dm_draw(rankdir = "LR", view_type = "all")
```

<br><br>

# Out-of-Network Files

<br>

```{r}
centene_oon_urls <- centene_toc_resp |> 
                    dplyr::filter(type == "out_of_network") |> 
                    dplyr::select(location) |> 
                    dplyr::distinct() |> 
                    tibble::deframe()
```


```{r echo=FALSE}
centene_oon_urls
```
<br><br>

```{r}
centene_oon_files <- centene_oon_urls |> 
                     purrr::map_dfr(defog_oon)
```

```{r echo=FALSE}
centene_oon_files
```


```{r}
dm_centene_oon <- dm::dm(centene_oon_files)
dm::dm_enum_pk_candidates(dm = dm_centene_oon, table = centene_oon_files)
```

<br><br>

# In-Network Files

<br>

```{r}
centene_inn_urls <- centene_toc_resp |> 
                    dplyr::filter(type == "in_network") |> 
                    dplyr::select(location) |> 
                    dplyr::distinct() |> 
                    tibble::deframe()
```


```{r echo=FALSE}
centene_inn_urls
```

<br>

```{r}
# centene_inn_files <- centene_inn_urls |> 
#                      purrr::map_dfr(defog_inn)
```

```{r echo=FALSE}
# centene_inn_files
```
